\documentclass[11pt]{article}

\usepackage[margin=0.8in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{array}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{needspace}
\usepackage[table]{xcolor}
\usepackage[natbibapa]{apacite}

\definecolor{PrimaryRed}{HTML}{8B1E1E}
\definecolor{SoftBlue}{HTML}{DDEEFF}
\definecolor{SoftGreen}{HTML}{E7F2E8}
\definecolor{SoftGold}{HTML}{FFF2CC}
\definecolor{SoftGray}{HTML}{F4F4F4}

\hypersetup{colorlinks=true,linkcolor=black,urlcolor=black,citecolor=black}
\setlength{\parindent}{0pt}
\setstretch{1.12}
\bibliographystyle{apacite}

\begin{document}

\begin{titlepage}
\thispagestyle{empty}
\begin{center}
{\large University of Rochester\\}
{\normalsize Warner School of Education\\[0.18in]}

{\color{PrimaryRed}\rule{\textwidth}{1.4pt}}\\[0.18in]
{\Huge\bfseries Many Ways to Be a Good Classmate}\\[0.18in]
{\LARGE A Kit for Kids Lesson on Peer Belonging, Communication, and Support}\\[0.22in]
{\Large EDE 448 --- Module 1}\\[0.35in]

\colorbox{SoftBlue}{%
\parbox{0.88\textwidth}{%
\centering\normalsize
\textbf{From Peer Help to Peer Access}\\[0.07in]
A placement-informed 10-minute peer-education lesson using OAR resources to help students practice five concrete actions: invite, wait, ask, respect, and include.
}%
}
\end{center}

\vfill

\renewcommand{\arraystretch}{1.25}
\begin{center}
\begin{tabular}{>{\bfseries\RaggedLeft\arraybackslash}p{1.75in} >{\RaggedRight\arraybackslash}p{4.9in}}
Student & Piter Zacari Garcia Bautista \\
Assignment & Teach a Kit for Kids Lesson \\
Course & EDE 448 --- Communication and Positive Behavioral Supports for Students with Autism and Other Complex Needs \\
Primary Resources & OAR Kit for Kids, \textit{What's Up with Nick?}, and Friendship Tip Sheets \\
Teaching Context & Grade 2 technology classroom scenario grounded in non-identifying placement observations \\
Course Theme & Communication as access to dignity, agency, participation, and belonging \\
Submission Date & July 2026 \\
\end{tabular}
\end{center}

\vfill

\begin{center}
\begin{minipage}{0.9\textwidth}
\centering\large\itshape
Inclusion is not only being present in the same room. It means students can communicate, participate, make choices, receive support without shame, and belong.
\end{minipage}
\end{center}
\end{titlepage}

\Needspace{5\baselineskip}
{\Large\bfseries\color{PrimaryRed} Requirement Connection and Teaching Context}\par

The assignment requires the use of Organization for Autism Research educator materials to teach a 10-minute lesson to a grade-level student about understanding and supporting autistic classmates. The submission must provide a lesson summary, a reflection on how the lesson went, and a discussion of how the resources could be incorporated into a future classroom. This paper addresses each requirement directly.

I used OAR's Kit for Kids materials because they translate autism acceptance into language that elementary students can understand. The core story, \textit{What's Up with Nick?}, presents an autistic student through a classmate's perspective, while the Friendship Tip Sheets turn broad ideas such as kindness and acceptance into concrete peer actions \citep{oar2026kit,oar2026nick,oar2026tips}. I adapted the materials so the lesson would not suggest that one autistic character represents every autistic person. I emphasized that autism is one way a brain can work and that autistic students may communicate, move, learn, regulate, or experience the environment in many different ways.

I designed the lesson for a Grade 2 technology setting because my placement repeatedly showed that peer support becomes visible during coding, robotics, and collaborative building. Students needed help with login sequences, links, unfamiliar programs, materials, noise, turn-taking, and uneven pacing. In one placement transcript, a student who already knew how to enter a program was encouraged to help classmates who were still struggling. Later, a student questioned whether a visitor counted as a classmate, and the response emphasized that the person should still be included and should not be made to feel bad \citep{placement2026robotics}. Those observations made belonging a real classroom problem to examine rather than an abstract value.

\begin{center}
\colorbox{SoftGray}{%
\parbox{0.92\textwidth}{%
\textbf{Central lesson claim:} A supportive classmate does not decide what another student can do. A supportive classmate helps create the time, space, communication access, and invitation that allow the other student to participate with dignity and choice.
}%
}
\end{center}

\Needspace{5\baselineskip}
{\Large\bfseries\color{PrimaryRed} Summary of the 10-Minute Lesson}\par

The lesson was titled \textit{Many Ways to Be a Good Classmate}. The student-friendly goal was: \textit{I can name two ways to include and support a classmate who communicates, learns, moves, or experiences the room differently.}

I began with a visible first/next/last sequence so students knew what to expect. First, we would learn one idea about autism. Next, we would practice with a familiar classroom situation. Last, students would choose one supportive action they could use. This structure reflected what I observed in my placement: young learners were more successful when directions were short, sequenced, visible, and connected to an immediate task.

\renewcommand{\arraystretch}{1.35}
\begin{center}
\begin{tabular}{>{\bfseries\centering\arraybackslash}p{0.95in} >{\RaggedRight\arraybackslash}p{2.55in} >{\RaggedRight\arraybackslash}p{3.25in}}
\toprule
Time & Teaching move & Purpose \\
\midrule
0--2 min & Preview first/next/last and introduce autism as one way a brain can work. & Reduce uncertainty and avoid presenting autism as a tragedy or a single story. \\
2--4 min & Explain that communication may include speech, gestures, writing, pictures, AAC, movement, or silence. & Normalize different communication forms and processing needs. \\
4--8 min & Teach five peer actions and practice a technology-class scenario. & Move from general kindness to observable supportive behavior. \\
8--10 min & Complete: ``One way I can be a supportive classmate is... because...'' & Check whether students can connect an action to access or belonging. \\
\bottomrule
\end{tabular}
\end{center}

Using the OAR friendship guidance, I taught five actions:

\begin{enumerate}
\item \textbf{Invite} a classmate without forcing participation.
\item \textbf{Wait} so the person has time to process, communicate, or try.
\item \textbf{Ask} respectfully instead of guessing what someone needs.
\item \textbf{Respect} sensory needs, personal space, communication tools, breaks, and privacy.
\item \textbf{Include} students who are new, quiet, tired, or participating differently as full members of the group.
\end{enumerate}

The main practice scenario was based on placement patterns: during a coding activity, one student already knew how to enter the program, several classmates were still stuck, and another learner was new to the group and not following every step. I asked what a supportive classmate could do.

The responses focused on showing one step without grabbing the Chromebook, using a calm voice, waiting for the learner to try, helping classmates who were still circling or confused, and treating the new learner as part of the class. The most important distinction was between helping and taking over. A peer could point to the next button, repeat one direction, or ask whether help was wanted, but the device and decision-making should remain with the learner.

I closed with the sentence frame: \textit{One way I can be a supportive classmate is... because...} The purpose of the word ``because'' was to move students beyond naming a rule. They needed to explain how an action could reduce stress, increase access, protect dignity, or help someone belong.

\newpage
\Needspace{5\baselineskip}
{\Large\bfseries\color{PrimaryRed} Reflection on the Lesson}\par

The strongest part of the lesson was its connection to ordinary classroom behavior. Students often understand that they should be ``nice,'' but that word is too general to guide them during noise, frustration, partner work, login confusion, unequal pacing, or group cleanup. The lesson gave those moments usable language: help without taking over, wait without rushing, ask without assuming, respect without isolating, and include without forcing.

The placement evidence made the reflection more honest. In technology-rich classrooms, student competence can be hidden by login friction, unclear click paths, reading demands, sensory load, role ambiguity, or the pace of a partner. A student who pauses, repeats a question, moves away, watches before joining, or refuses a material may be communicating confusion, overload, uncertainty, or a need for more predictable access. Those reactions should not automatically be interpreted as inability, disrespect, or lack of interest.

\renewcommand{\arraystretch}{1.35}
\begin{center}
\begin{tabular}{>{\bfseries\RaggedRight\arraybackslash}p{1.65in} >{\RaggedRight\arraybackslash}p{2.45in} >{\RaggedRight\arraybackslash}p{2.7in}}
\toprule
What classmates may notice & A richer interpretation & A supportive response \\
\midrule
A delayed answer & The learner may need processing time or another communication mode. & Wait, offer choices, and notice gestures, writing, AAC, movement, or silence. \\
Moving away or covering ears & Noise, crowding, or sensory load may be too high. & Lower the volume, create space, and ask before touching or following. \\
Difficulty entering a coding task & Login steps, reading load, or unclear directions may be hiding competence. & Show one step, keep the device with the learner, and allow the learner to try. \\
A new or quiet student remains outside the group & Belonging may not yet be socially established. & Invite without pressure and explicitly treat the person as part of the class. \\
\bottomrule
\end{tabular}
\end{center}

The lesson also showed me that peer culture is part of positive behavioral support. If the classroom teaches students to invite, wait, ask, respect, and include, support does not rest only on the teacher or on the autistic student. Peers learn that access is something the whole classroom helps create. Autistic students and students with other complex support needs should not have to earn belonging by appearing typical, responding quickly, tolerating sensory discomfort, or repeatedly explaining why they need something different.

The part I would revise is pacing. Ten minutes was enough for one core idea and one realistic scenario, but it was not enough for a deep conversation about communication differences, sensory needs, privacy, consent, and the wide range of autistic experiences. I would keep the introductory lesson short, then revisit one action before each partner-heavy activity. Before robotics, I would review ``wait and ask.'' Before partner coding, I would review ``help without taking over.'' Before collaborative building, I would review ``include and respect space.'' The OAR language would become part of repeated classroom routines rather than a one-time presentation.

\Needspace{5\baselineskip}
{\Large\bfseries\color{PrimaryRed} Puzzle Plan and EQUITAS Alignment}\par

This lesson connects directly to my Puzzle Plan and EQUITAS goals. The \textbf{Puzzle Plan} is my interdisciplinary framework for combining lived experience, educational practice, classroom evidence, data, and research instead of relying on one isolated explanation. \textbf{EQUITAS} is the equity-focused lens within that framework; it asks whose knowledge is included, what context is missing, and where power or bias may shape a decision.

Through this lens, no diagnosis, behavior, observation, or peer comment should stand alone. Each is one piece of a larger picture. If a student does not answer immediately, the stronger question is not simply, ``Why are they ignoring me?'' It is, ``What communication option, wait time, sensory support, relationship move, or environmental change might increase access?'' If a learner does not join a partner task, the goal is not to force visible compliance. The goal is to understand whether the barrier involves communication, sensory load, uncertainty, trust, task design, or the social behavior of peers.

This is also why I treated the OAR materials as a starting point rather than a complete account of autistic experience. Kit for Kids offers accessible peer language, but an equitable classroom still needs autistic-authored perspectives, student communication, family knowledge, and direct observation of what helps each learner participate. The goal is not pity, charity, or making a student easier for the system. The goal is access, dignity, agency, participation, and belonging.

\Needspace{5\baselineskip}
{\Large\bfseries\color{PrimaryRed} Future Classroom Incorporation}\par

In my future classroom, I would use Kit for Kids during beginning-of-year community building and revisit the materials before coding, robotics, group projects, recess transitions, digital publishing, project showcases, and partner troubleshooting. These are moments when students must coordinate language, space, noise, materials, timing, and emotion. They are also moments when misunderstanding can become teasing, taking over, exclusion, or the assumption that another student is being difficult.

I would pair the OAR resources with supports available to the whole class: first/next/last directions, visual choices, quiet options, clear partner roles, help cards, predictable wait time, permission to pass, and multiple ways to respond. These supports should not appear only after one learner struggles or discloses a diagnosis. They should be part of the classroom's normal design.

I would also make the five peer actions visible near collaborative work areas. The classroom message would be that invitation must include consent, help should preserve ownership, waiting is an active form of respect, sensory tools are not toys, and different participation is still real participation. When developmentally appropriate, I would include autistic-authored or autistic-led perspectives so students do not learn about autism only through non-autistic interpretation.

\begin{center}
\colorbox{SoftGreen}{%
\parbox{0.92\textwidth}{%
\textbf{Future classroom commitment:} I will teach peer inclusion proactively, before conflict or exclusion occurs, and I will evaluate support by whether it expands communication, choice, competence, and belonging.
}%
}
\end{center}

\newpage
\Needspace{5\baselineskip}
{\Large\bfseries\color{PrimaryRed} Conclusion}\par

OAR's Kit for Kids materials provided a developmentally appropriate way to teach peer support inside ordinary classroom moments. The placement evidence helped me make the scenario realistic and reminded me that behavior cannot be separated from environment, communication access, sensory conditions, and peer relationships.

My main takeaway is that positive behavioral support includes peer culture. A classroom should already know how to invite, wait, ask, respect, and include before harm happens. Autistic students and students with other complex support needs should not have to become more typical in order to be recognized as competent classmates. The classroom must become more responsive, curious, and flexible so that different ways of communicating, moving, learning, and participating are treated as part of belonging.

\newpage
\small
\bibliography{references}

\end{document}
