\reviewsection{Requirement Connection and Teaching Context}

The assignment requires the use of Organization for Autism Research educator materials to teach a 10-minute lesson to a grade-level student about understanding and supporting autistic classmates. The submission must provide a summary of the lesson, a reflection on the lesson, and a discussion of how the resources could be incorporated into a future classroom. This paper addresses those requirements directly and uses visual diagrams to connect lesson design, classroom evidence, and future practice.

I used OAR's Kit for Kids materials because they translate autism acceptance into language elementary students can understand. The core story, \textit{What's Up with Nick?}, presents an autistic student through a classmate's perspective, while the Friendship Tip Sheets turn broad ideas such as kindness and acceptance into concrete peer actions \citep{oar2026kit,oar2026nick,oar2026tips}. I emphasized that autism is one way a brain can work and that autistic students may communicate, move, learn, regulate, or experience the environment in many different ways.

I designed the lesson for a Grade 2 technology setting because my placement repeatedly showed that peer support becomes visible during coding, robotics, and collaborative building. Students needed help with login sequences, links, unfamiliar programs, materials, noise, turn-taking, and uneven pacing. In one transcript, a student who knew how to enter a program was encouraged to help classmates who were still struggling. Later, a student questioned whether a visitor counted as a classmate, and the response emphasized that the person should still be included and should not be made to feel bad \citep{placement2026robotics}.

\begin{figure}[htbp]
\centering
\resizebox{0.96\textwidth}{!}{\begin{tikzpicture}[box/.style={rounded corners=3mm,draw=black!55,thick,minimum width=2.2in,minimum height=0.78in,align=center},arrow/.style={-{Latex[length=3mm]},very thick,draw=black!60}]
\node[box,fill=SoftBlue] (a) {\textbf{OAR resources}\\peer language and friendship actions};
\node[box,fill=SoftGreen,right=8mm of a] (b) {\textbf{Placement evidence}\\noise, pacing, login friction, belonging};
\node[box,fill=SoftGold,right=8mm of b] (c) {\textbf{Lesson design}\\concrete choices peers can practice};
\node[box,fill=SoftLavender,right=8mm of c] (d) {\textbf{Access-to-agency}\\dignity, choice, participation, belonging};
\draw[arrow] (a)--(b); \draw[arrow] (b)--(c); \draw[arrow] (c)--(d);
\end{tikzpicture}}
\caption{Visual source bridge connecting OAR resources, placement evidence, lesson design, and the access-to-agency goal.}
\label{fig:source-bridge}
\end{figure}

Figure~\ref{fig:source-bridge} shows that the lesson was not created from one source. OAR provided developmentally appropriate language, placement evidence showed where misunderstandings occurred, and the lesson translated both into actions students could use during real routines.
